Authentication based on DRAM PUFs

### 2021-06-17 latexPaper/paper.tex
first draft finished

% Write abstract here
\begin{abstract}
The short abstract (50-80 words) is intended to give the reader an overview of the work.
Keep in mind that he does not known the work yet.
\end{abstract}

@@

\[ HD_{frac}(a,b) = \dfrac{HD(a,b)}{|a|} \]
\[ J(a,b) = \dfrac{| a \bigcap b |}{| a \bigcup b |} \]

@@

When a PUF cannot generate a large CRP database, it is used with a Fuzzy Extractor a.k.a Helper Data System \cite{HDS15} for secure key storage. A fuzzy extractor correct errors in the PUF response \cite{SUT18} and enables regeneration of a cryptogrpahic key. A general construction of a fuzzy extractor contains:

@@

One of the earliest implementations of fuzzy extractors is the Code Offset Method. \cite{COM} COM uses a error correcting code at the core of its construction. The helper data \(w = X \oplus Enc(k)\), where \(Enc()\) is the encoding function of the error correcting code. The reconstructed key \(k' = Dec(X' \oplus w)\), where \(Dec()\) is the decoding function of the error correcting code. The important point to note here is that \(w\) plays the role of a syndrome. The error correcting code extracts the key \(k\) by correcting errors in \(X'\). This is clear when the formula is rewritten as \(k' = Dec(X' \oplus X \oplus Enc(k))\). Any remaining bits of the \(X' \oplus X\) if there are is corrected by \(Dec()\)

[insert fuzzy extractor image]

@@

Another version of the COM scheme, Syndrome-COM or SCOM,\cite{COM} leverages syndrome decoding to use the input \(X\) itself as the cryptographic key. In this scheme the helper data \(w = Syn(X)\), where \(Syn()\) is the syndrome function. The reconstructed key \(k' = SynDec(w \oplus Sync(X'))\). The expression \(w \oplus Sync(X')\) equals \(Syn(X \oplus X')\), i.e., the syndrome of the error vector and \(SynDec()\) is teh syndrom decoder which corrects the error.

@@

\section{Conclusion}
This section summarizes the paper. Now the reader knows your work, you can go into detail a little bit more about the main aspects.

@@

    \bibitem{COM}
    Skoric, B., & Vreede, de, N. (2014). The spammed code offset method. IEEE Transactions on Information Forensics and Security, 9(5), 875-884. https://doi.org/10.1109/TIFS.2014.2312851

>>>>

% Write abstract here
\begin{abstract}
Security concerns relating to IoT are increasing and the most prominent of these concerns is that of counterfeit or tampered hardware. For such a problem, it is important to employ a hardware-intrinsic security mechanism for authentication of the device. While previous solutions like secure key storage attempt to solve this problem they only pass on the issue to the next stage. This paper outlines the use of Physically Unclonable Functions (PUFs) for hardware-intrinsic authentication. It summarizes well-known works on DRAM based PUFs and also presents known protocols and schemes to achieve authentication on embedded devices using PUFs.
\end{abstract}

@@

\[ HD_{frac}(a,b) = \dfrac{HD(a,b)}{|a|} \quad\text{and}\quad J(a,b) = \dfrac{| a \bigcap b |}{| a \bigcup b |} \]

@@

When a PUF cannot generate a large CRP database, it is used with a Fuzzy Extractor a.k.a Helper Data System \cite{HDS15} for secure key storage. A fuzzy extractor corrects errors in the PUF response \cite{SUT18} and enables regeneration of a cryptogrpahic key. This way the reproduced key can be used to setup a secure channel through symmetric protocols. Once a secure channel is established authentication can be done through asymmetric protocols. A general construction of a fuzzy extractor contains:

@@

\begin{figure}[!hbt]
    % Center the figure.
    \begin{center}
    % Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
    \includegraphics[scale=0.45]{figs/COM.png}
    % Create a subtitle for the figure.
    \caption{Fuzzy Extractor}
    % Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
    \label{fig:tf_plot}
    \end{center}
\end{figure}

One of the earliest implementations of fuzzy extractors is the Code Offset Method. \cite{COM} COM uses a error correcting code at the core of its construction. The helper data \(w = X \oplus Enc(k)\), where \(Enc()\) is the encoding function of the error correcting code. The reconstructed key \(k' = Dec(X' \oplus w)\), where \(Dec()\) is the decoding function of the error correcting code. The important point to note here is that \(w\) plays the role of a syndrome. The error correcting code extracts the key \(k\) by correcting errors in \(X'\). This is clear when the formula is rewritten as \(k' = Dec(X' \oplus X \oplus Enc(k))\). Any remaining bits of the \(X' \oplus X\), if there are any, is corrected by \(Dec()\)

@@

Another version of the COM scheme, Syndrome-COM or SCOM,\cite{COM} leverages syndrome decoding to use the input \(X\) itself as the cryptographic key. In this scheme the helper data \(w = Syn(X)\), where \(Syn()\) is the syndrome function. The reconstructed key \(k' = SynDec(w \oplus Syn(X'))\). The expression \(w \oplus Syn(X')\) equals \(Syn(X \oplus X')\), i.e., the syndrome of the error vector and \(SynDec()\) is teh syndrom decoder which corrects the error.

@@

\section{Conclusion}
This paper highlights why and how PUFs fufill the demands of hardware-intrinsic authentication. It explains the well known methods of implementing PUFs on DRAMs and the advantages of DRAM PUFs. It outlines the objectives a PUF implementation has to meet in order to be fit for use in authentication. It summarizes a simple lightweight protocol that can meet strict resource constraints for embedded processors. It also dives into the details of using PUFs for secure key storage using helper data systems (HDS) and summarizes different constructions for HDS.

@@

    \bibitem{COM}
    Skoric, B., \& Vreede, de, N. (2014). The spammed code offset method. IEEE Transactions on Information Forensics and Security, 9(5), 875-884. https://doi.org/10.1109/TIFS.2014.2312851
